Volunteers in the Clouds: A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2016-01-10 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
Reviewing the abstract
And adding the note to the response. Refs #85

Using the browser as a computing resource in volunteer computing has presented several advantages, 
but it remains a challenge to fully harness both the users’ behaviour and the browser’s capabilities.
That is why we have enhanced {\sf NodIO}, a framework used to create client-server architectures 
for distributed evolutionary algorithms, resulting in {\sf NodIO-W$^2$}, which we present in this paper.
{\sf NodIO-W$^2$} leverages the HTML5 Web Workers specification to execute in the background several clients per
browser, so that the the number of generations per user could be improved. The enhancements on the NodIO architecture,
along with some initial results on the expected performance and scaling behavior when the number of users is increased,
are introduced. We also use the algorithm data to find out what kind of patterns the user behavior follows by examining 
the resources they devote to our experiment, and try to fit them in some statistical distribution. In general, 
our experiments prove, first, that {\sf NodIO} is a flexible and low-overhead platform to perform distributed computation
experiments that include volunteers, and then that user behavior follows some patterns, and, thus, are amenable to a model.
% Volunteer computing is extensively used in science and industry, but
% it still has a long way to go in order to become a mainstream
% technology in the same way the cloud technologies in general are. %I have changed "have" to "are"
% The lack of general purpose and open
% source tools with built-in analytics could be one of the reasons of
% why this is so, as well as the lack of proofs of concept.
% % (Paloma) The following sentence is way too long, and the "which" after "Javascript" is confusing, so one does not know if the which refers to the framework or Javascript by reading the whole sentence.
% % I propose: "That is why in this paper we present NodIO, a framework used to create client-server architectures for distributed evolutionary algorithms, entirely written in JavaScript. Our framework needs minimal server support to work and is able to support persistent, asynchronous, distributed evolutionary algorithms running in the browser, as well as any other client consuming its REST application programming interface."
% That is why
% in this paper we present {\sf NodIO}, a framework used to create
% client-server architectures for distributed evolutionary algorithms,
% entirely written in JavaScript, which needs minimal server support to
% work and that is able to support persistent, asynchronous, distributed
% evolutionary algorithms running in the browser, as well as any other
% client consuming its REST application programming interface. An
% enhanced implementation, which we have called {\sf NodIO-W$^2$}, is
% also presented; this version leverages the HTML5 Web Workers
% specification to execute several clients per browser and do it in the
% background, so that the the number of generations per user could be
% improved. The architecture, along with some initial results on the
% expected performance and scaling behavior when the number of users is
% increased is introduced. % (Paloma) I've changed this "presented" for a synonym
% We also use the algorithm data to find out
% what kind of patterns the user behavior follows by examining the
% resources they devote to our experiment, and try to fit them in % (Paloma) Changed. Phrasal verb was wrong.
%  some
% statistical distribution to create the bases of a model of user
% behavior in volunteer computing experiments of this kind that can be
% used by researchers to predict their performance. %(Paloma) Changed to "their" because of "experiments"
% In general, our
% experiments prove, first, that {\sf NodIO} is a flexible and
% low-overhead platform to perform distributed computation experiments
% that include volunteers, and then that user behavior follows some
% patterns, and, thus, are amenable to a model.
\end{abstract}

>>>>

Using the browser as a computing resource in volunteer computing has presented several advantages, 
but it remains a challenge to fully harness both the users’ behaviour and the browser’s capabilities.
That is why we have enhanced {\sf NodIO}, a framework used to create client-server architectures 
for distributed evolutionary algorithms, resulting in {\sf
  NodIO-W$^2$}, whose results we present in this paper.
{\sf NodIO-W$^2$} leverages the HTML5 Web Workers specification to execute in the background several clients per
browser, so that the the number of generations per user could be improved. The enhancements on the NodIO architecture,
along with some initial results on the expected performance and scaling behavior when the number of users is increased,
are introduced. We also use the algorithm data to find out what kind of patterns the user behavior follows by examining 
the resources they devote to our experiment, and try to fit them in some statistical distribution. In general, 
our experiments prove, first, that {\sf NodIO} is a flexible and low-overhead platform to perform distributed computation
experiments that include volunteers, and then that user behavior
follows some patterns, and, thus, are amenable to a model and thus predictable.
% Volunteer computing is extensively used in science and industry, but
% it still has a long way to go in order to become a mainstream
% technology in the same way the cloud technologies in general are. %I have changed "have" to "are"
% The lack of general purpose and open
% source tools with built-in analytics could be one of the reasons of
% why this is so, as well as the lack of proofs of concept.
% % (Paloma) The following sentence is way too long, and the "which" after "Javascript" is confusing, so one does not know if the which refers to the framework or Javascript by reading the whole sentence.
% % I propose: "That is why in this paper we present NodIO, a framework used to create client-server architectures for distributed evolutionary algorithms, entirely written in JavaScript. Our framework needs minimal server support to work and is able to support persistent, asynchronous, distributed evolutionary algorithms running in the browser, as well as any other client consuming its REST application programming interface."
% That is why
% in this paper we present {\sf NodIO}, a framework used to create
% client-server architectures for distributed evolutionary algorithms,
% entirely written in JavaScript, which needs minimal server support to
% work and that is able to support persistent, asynchronous, distributed
% evolutionary algorithms running in the browser, as well as any other
% client consuming its REST application programming interface. An
% enhanced implementation, which we have called {\sf NodIO-W$^2$}, is
% also presented; this version leverages the HTML5 Web Workers
% specification to execute several clients per browser and do it in the
% background, so that the the number of generations per user could be
% improved. The architecture, along with some initial results on the
% expected performance and scaling behavior when the number of users is
% increased is introduced. % (Paloma) I've changed this "presented" for a synonym
% We also use the algorithm data to find out
% what kind of patterns the user behavior follows by examining the
% resources they devote to our experiment, and try to fit them in % (Paloma) Changed. Phrasal verb was wrong.
%  some
% statistical distribution to create the bases of a model of user
% behavior in volunteer computing experiments of this kind that can be
% used by researchers to predict their performance. %(Paloma) Changed to "their" because of "experiments"
% In general, our
% experiments prove, first, that {\sf NodIO} is a flexible and
% low-overhead platform to perform distributed computation experiments
% that include volunteers, and then that user behavior follows some
% patterns, and, thus, are amenable to a model.
\end{abstract}
